---
title: Email Report
output: 
  html_document:
    code_folding: hide
params:
  symbol: TSLA
  threshold: 10
  force: True
---
  
# Report for `r params$symbol` on `r Sys.Date()`

## Summary{.tabset}

```{r, echo=TRUE, message=FALSE}
library(quantmod)
library(DT)
library(highcharter)
library(blastula)
library(formattable)
library(ggplot2)
library(ggthemes)

prices <- round(getSymbols(params$symbol, auto.assign = FALSE, src = 'yahoo'), 2)
close <- Cl(last(prices))
open <- Op(last(prices))

recent <- last(prices, n=90)
recent_nv <- recent[,-5]

```

The stock closed `r ifelse(close>open,'up','down')` at `r close` dollars per share yesterday.


### Price History

The chart below is made with the `quantmod` and `highcharter` R packages. An API returns all of the price history based on the stock tick symbol provided as a parameter. The candlestick chart is a default function from highcharter, as is the Economist theme.


```{r echo=TRUE, warning=FALSE, message=FALSE}

highchart(type = "stock") %>% 
   hc_yAxis_multiples(
    list(title = list(text = NULL), height = "75%", top = "0%"),
    list(title = list(text = NULL), height = "15%", top = "80.5%", opposite = TRUE)
  ) %>%
  hc_add_series(prices, type = "candlestick", yAxis=0, name= params$symbol) %>% 
  hc_add_series(prices[,paste0(params$symbol,".Volume")], name="Volume", type="column", yAxis=1) %>% 
  hc_add_theme(hc_theme_economist())
```

### Raw Data

The table below displays the daily price data for the stock. A concise, interactive table is created with the `DT` package. 

  
```{r echo=TRUE}
df <- as.data.frame(recent)
df[,paste0(params$symbol, ".Volume")] <- df[,paste0(params$symbol, ".Volume")]/1000000 
datatable(df) %>% 
  formatCurrency(c(paste0(params$symbol, ".Open"), paste0(params$symbol, ".High"), paste0(params$symbol, ".Low"), paste0(params$symbol,".Close")), digits=2) %>% 
  formatRound(c(paste0(params$symbol, ".Volume")), digits=0)
```

## Legacy Information

This report also creates an excel file with the relevant information updated by R. The Excel file contains a legacy report that will slowly be replaced.

```{r echo=TRUE}
fname <- sprintf('%s.xlsx', Sys.Date())
write.csv(df, file = fname)
rmarkdown::output_metadata$set(rsc_output_files = list(fname))
```

[Link to Excel](`r fname`)

## Email

This report also produces an email that is sent to key stakeholders with summary information if the price change is above `r params$threshold`.

```{r warning = FALSE, message = FALSE, echo = TRUE}
# Calculate the total change
close <- Cl(last(prices, n = 2))
diff <- round(as.numeric(close[2]) - as.numeric(close[1]),2)

# If the change is above a $10 / share, send an email to stake holders
if (abs(diff) > params$threshold || params$force) {
  rmarkdown::output_metadata$set(rsc_email_suppress_scheduled = FALSE)
  
  # get metadata
  report_name <- Sys.getenv("RSC_REPORT_NAME")
  report_url <- Sys.getenv("RSC_REPORT_URL")
  subscription_url <- Sys.getenv("RSC_REPORT_SUBSCRIPTION_URL")
  
  # set a dynamic subject line
  subject <- paste0(params$symbol,
                    ' is ', 
                    ifelse(diff > 0, 'up', 'down'), 
                    ' today by $', 
                    abs(diff), '!')
  rmarkdown::output_metadata$set("rsc_email_subject" = subject)
  
  # also update the body
  price_new <- prices[,c(1,4)]
  colnames(price_new) <- c('open', 'close')
  price_new$change <- price_new$close - price_new$open
  tbl <- format_table(
    x = as.data.frame(tail(price_new)),
    list(
      change = formatter("span", style = x ~ ifelse(x > 0, style(color = "green"), style(color = "red"))),
      area(col = c(open, close)) ~ normalize_bar("lightgrey")

    )
  )
  
  
  p <- recent[,6] %>% 
    autoplot() +
    geom_smooth() +
    theme_fivethirtyeight() + 
    labs(
      title = sprintf("%s Price Adjusted", params$symbol)
    )
  
  msg <- compose_email(
    body = "
    Hello Team,
    
    Here are the latest stock prices for {params$symbol}.
    

    {tbl}

    The historical trend is shown below: 


    {add_ggplot(p, width = 6, height = 6)}
    

    Let me know if you have any questions.
    

    Best,
    

    Team Lead",
    footer = "
    This <strong>{report_name}</strong> document is available on our RStudio Connect server [here]({report_url}).

    To stop receiving these emails, <code>[unsubscribe]({subscription_url})</code>.
    "
  )
  rmarkdown::output_metadata$set(rsc_email_body_html = msg$html_str)
  rmarkdown::output_metadata$set(rsc_email_images = msg$images)
  
  # attach the excel file
  rmarkdown::output_metadata$set(rsc_email_attachments = list(fname))
  
} else {
  # don't send an email
  rmarkdown::output_metadata$set(rsc_email_suppress_scheduled = TRUE)
}

```
